Project Protocol

### 2019-10-21 protocol.Rmd

##	Data analysis and Statistical methods

This will be analysed using a generalised linear model, with random effects capturing the differences between the 100 participants.
The main effects used will consider the spatial distribution of the errors, gender, degree education level achieved, age range and whether the participant has lived in Australia.

Each lineup will have similar hypotheses:
$H_0:$ there is no real structure visible in the data plot
$H_1:$ there is real structure visible in the data plot

>>>>

##	Data analysis and statistical methods

The results will be analysed using a generalised linear model, with a subject random effect. There will be two main effects: plot type and trend model.

Each lineup has the same hypotheses:
$H_0:$ there is no real structure visible in the data plot
$H_1:$ there is real structure visible in the data plot
